
\documentclass[a4paper,10pt]{article}
%SetFonts
% libertine+newtxmath
\usepackage[osf]{libertine} %loads biolinum ss, similar to optima
\usepackge[T1]{fontenc}
\usepackage{textcomp}
\usepackage[varqu,varl]{inconsolata} %tt
\usepackage{amsmath,amsthm}
\usepackage[libertine,bigdelims,vvarbb]{newtxmath}
\usepackage[cal=boondoxo]{mathalfa} % less slanted than STIX
\usepackage[supstfm=libertinesups,%
  supscaled=1.2,%
  raised=-.13em]{superiors}
%SetFonts
%SetFonts
% Lucida Bright complete
\usepackage{amsmath}%must come before lucidabr
\us9epackage[T1]{fontenc}% must come before lucidabr to get correct accents
\usepackage{textcomp} % to get the right copyright, etc.
%must load fontenc before lucidabr, or no \mathfrak
\usepackage[expert,vargreek,altbullet]{lucidabr}%use \mathbf,\mathfrak
\DeclareEncodingSubset{TS1}{hlh}{1}  % including \oldstylenums
\usepackage{mathalfa} %set math alphabets here
%amsfonts, amssymb not needed
%SetFonts
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\setlist{nolistsep}


\begin{document}

\centerline{\huge \textbf{Lars Tischer}}
\smallskip
\noindent
\textbf{Address:} Muehlenweg 19, 21481 Lauenburg, Germany \\
\textbf{Email:} \href{mailto:larstischer@icloud.com}{larstischer@icloud.com} \\
\textbf{Phone:} +49 157 35 19 24 96 \\
\textbf{LinkedIn:} \href{https://www.linkedin.com/in/lars-tischer-5b9b13317/}{linkedin.com/in/lars-tischer-5b9b13317/}

\section*{Professional Summary}
I am a Senior Test Manager with 7 years of experience as Quality Authority in software development for medical technology. Expert in managing complex projects, leading cross-functional teams, and ensuring quality evidence prior to deadlines. Strong in strategic planning, requirement management, regulated product documentation, and fostering team collaboration.

\section*{Professional Experience}
\textbf{Quality Test Manager, System Integration} \\
OLYMPUS Surgical Technologies Europe, Hamburg, Germany \hfill \textit{04/2019 – 04/2024} 
\begin{itemize}
    \item Led design verification projects with 4 core team members plus externals.
    \item Managed the end-to-end software development process for medical technology.
    \item Strategically planned and directed all test activities.
    \item Developed test specifications, plans, and documentation.
    \item Implemented a state-of-the-art test lab, enhancing testing capabilities.
\end{itemize}

\textbf{Quality Test Engineer, System Integration} \\
OLYMPUS Surgical Technologies Europe, Hamburg, Germany \hfill \textit{08/2017 – 03/2019}
\begin{itemize}
    \item Engineered tests for medical products following the V-Model.
    \item Produced technical documentation and test cases.
    \item Conducted verification activities and facilitated project reviews.
\end{itemize}

\textbf{Service Technician} \\
YXLON International GmbH, Hamburg, Germany \hfill \textit{01/2014 - 09/2015}
\begin{itemize}
    \item Conducted global system installations for automotive industries.
    \item Delivered customer training and created comprehensive documentation.
\end{itemize}

\section*{Education}
\textbf{Web and App Development Bootcamp} \\
WBS Coding School \hfill \textit{02/2025 - 06/2025} 

\textbf{Artificial Intelligence for Business Bootcamp} \\
WBS Coding School \hfill \textit{12/2024 - 02/2025} 

\textbf{Master of Science in Electrical and Electronic Engineering} \\
Glyndwr University, Wrexham, United Kingdom \hfill \textit{05/2016 - 07/2017} 

\textbf{Bachelor of Engineering in Electrical and Electronic Engineering} \\
Glyndwr University, Wrexham, United Kingdom \hfill \textit{09/2015 - 05/2016}

\section*{Skills and Certifications}
\textbf{Leadership Skills:}
\begin{itemize}
    \item Team Management
    \item Strategic Planning
    \item Project Management
\end{itemize}

\textbf{Certifications:}
\begin{itemize}
    \item ISTQB Test Manager – Advanced Level
    \item IREB Certified Professional for Requirements Engineering
\end{itemize}

\textbf{Technical Knowledge:}
\begin{itemize}
    \item ISO 9000ff., ISO 13485, FDA-QSR
    \item Power Electronics, Automation Technology
\end{itemize}

\section*{Languages}
\begin{itemize}
    \item \textbf{German:} Native
    \item \textbf{English:} Fluent (C1 level)
\end{itemize}

\section*{Passion}
Jesus, Technology, Writing, Cycling (Instagram: @workbikebalance\_)
\end{document}
